Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-24 article.tex
first pass discussion without reference sand elaboration

This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of graphical models. These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing. A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting the critical nature that water use plays. As one of the most interconnected variables, the influence of water use reaches almost every variable, with its connection to operational decisions being reflected within its connection to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil. This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.

Of further significance was the management of pests and diseases, market pressures and climate. With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use. Particularly, climate acted as an interface between water and pest/disease, due to it being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:. Of the greatest concern to climate is how it influences water availability, pest and disease pressures, and overall vineyard health. Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change TODO:. In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield, erosion, and are further determinants of chosen grape varieties TODO:. The BN models capture the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.

the case study highlighted the direct influence on environmental sustainability, where it was found to be the most sensitive to elements used in operational responses to factors such as disease through the use of agrochemicals. A major concern from the industry panel was, that while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts. The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately. TODO: A literature review regarding this does here TODO:

% The models indicated that effective pest and disease management can mitigate the need for extensive agrochemical use, thereby reducing the environmental footprint of viticulture. This interaction is crucial for developing integrated pest management strategies that are both effective and sustainable.

The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest and disease control, economic pressures, and climate conditions as key factors. However, the BN models provides structure to the broader way of how these factors interact, offering a clearer understanding of their interdependencies and relative importance. Many of these singular relationships are well defined within literature studies such as TODO:.

While the existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study. The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered. A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the Bn to be used as a framework that can further integrate other studies results into these relationships.

Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have a substantial impact on sustainability practices. The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers. The BN models helped to illustrate how economic incentives can be drivers of sustainable practices. The definitive influence and relationships between what are more tertiary considerations of environmental sustainability being more directly connected to further considerations such as operational costs; is a potential further avenue of research that would compliment this work greatly.

In summary, the interpretation of results from the Bayesian Network models enhances our understanding of environmental sustainability in viticulture by providing a detailed and structured analysis of key factors and their interactions. The findings underscore the importance of integrated management practices that consider the interconnected nature of water quality, pest and disease management, market pressures, agrochemical use, and climate conditions. By aligning with and expanding upon existing literature, this study offers valuable insights for both researchers and practitioners aiming to promote sustainability in viticulture.

@@

>>>>

This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of BNs created with assistance from industry input. These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing. A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical nature as one of the most interconnected variables. The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil. This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.

Of further significance was the management of pests and diseases, market pressures and climate. With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use. In particular, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:. Of great concern to climate was how it influenced water availability, pest/disease pressures, and its overall contribution to vineyard health. Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change TODO:. In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield, erosion, and are further determinants of chosen grape varieties TODO:. The BN models capture the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.

The case study highlighted the direct influences on environmental sustainability, where environmental sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors. A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts. The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately. TODO: A literature review regarding this does here TODO:.

The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest/disease control, economic pressures, and climate conditions as key factors. Many of these singular relationships are well-defined within literature studies such as TODO:.

The BN models provide structure to the broader way of how how the major factors within literature interact, offering a clearer understanding of their interdependencies and relative sensitivity with regard to environmental sustainability as an outcome. The existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study. The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered. A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships TODO:.

The BN models helped to illustrate how economic incentives can be drivers of sustainable practices. The definitive influence and relationships between what are more tertiary considerations of environmental sustainability being directly connected to further considerations such as operational costs. Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have an impact on sustainability practices but were limited in this study through only reviewing them within the lens of environmental sustainability. The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers as well as what may be much more specific circumstance; of which is a potential further avenue of research that would compliment this work significantly.

@@

The interpretation of results from the Bayesian Network models enhances our understanding of environmental sustainability in viticulture by providing a detailed and structured analysis of key factors and their interactions. The findings underscore the importance of integrated management practices that consider the interconnected nature of water quality, pest and disease management, market pressures, agrochemical use, and climate conditions. By aligning with and expanding upon existing literature, this study offers valuable insights for both researchers and practitioners aiming to promote sustainability in viticulture.
